Can greedy-like heuristics be useful for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization?

### 2020-10-10 doc/paper.tex
scaling of tables
some work

      After conducting preliminary results, for
        \textsc{Greedy + \textsc{Cplex}} we decided to set up $K = 0.05 \cdot n$.

     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
            \item and 4 heuristic approaches:
           \begin{itemize}
           	\item two pure greedy methods, guided by $g_1$ and $g_2$, labeled as \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item two \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy-1}+\textsc{Cplex} and 
            \textsc{Greedy-2}+\textsc{Cplex}. 
        \end{itemize}
    \end{itemize}

@@

     \begin{table}[]
     	\begin{tabular}{l|lllllll|}
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & 15.93  & 0.15    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 16.04  & 98.22   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 22.63  & 0.00    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
     		\textsc{Greedy-2}          & 19.97  & 0.00    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.07    & 21.19     & 2/97      & 0.30    & 57/97      & 0.06     \\
     		   \textsc{Greedy-2+Cplex} & 18.39  & 0.00    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
     	\end{tabular}
     \end{table}

      \begin{table}[]
      	\begin{tabular}{l|lllllll}
      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &  $ \bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & 36.03  & 0.00    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Cp}               & 36.03  & 18.95   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Greedy-1}             & 39.28  & 0.00    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
      		\textsc{Greedy-2}          & 40.92  & 0.00    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.01    & 19.41     & 4/97      & 0.21    & 19/97      & 0.08     \\
      		   \textsc{Greedy-2+Cplex} & 37.31  & 0.00    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
      	\end{tabular}
      \end{table}

     \begin{table}[]
     	\begin{tabular}{l|lllllll}
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & 2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
     		\textsc{Greedy-2}          & 3.52   & 0.32    & 6.61      & 2/97      & 0.10    & 28/97      & 0.08     \\
     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & 0.08    & 25/97      & 0.04     \\
     		   \textsc{Greedy-2+Cplex} & 3.32   & 0.33    & 6.81      & 6/97      & 0.08    & 25/97      & 0.04  \\ \hline   
     	\end{tabular}
     \end{table}

    \begin{table}[]
 	  \begin{tabular}{l|lllllll}
 		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
 		\textsc{Cplex}            & 6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Cp}               & 6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Greedy-1}             & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		\textsc{Greedy-2}          & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		   \textsc{Greedy-1+Cplex}  & 6.73   & 0.32    & 6.45      & 96/97     & 0.01    & 96/97      & 0.03     \\
 		   \textsc{Greedy-2+Cplex} & 7.42   & 0.31    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
 	\end{tabular}
   \end{table}

        From the numerical results, we observe the following conclusions:
        \begin{itemize}
        	\item  For the topollogically--based benchmarks and the exact approaches, \textsc{Cplex} achieved best results among other approaches. moreover, \textsc{Cplex} could prove optimallity of all (192) instances, while \textsc{Cp} could not. It is expecially noticed for small polygons, where it seems hard for \textsc{Cp} to prove optimality.
        	\item For the point--based benchmark set and the exact approaches, \textsc{Cplex} again show its power, since it could prove all instances to optimallity, which is also the case of \textsc{Cp}.
        	\item  For the topollogically--based benchmarks and the heuristic approaches\fxnote{TODO...}
        \end{itemize}
          \fxnote{TODO: generisati plotove za vremena svakog od algoritama (da se vidi da je greedy brzi -- nadamo se)}

>>>>

      After conducting preliminary results, for
        \textsc{Greedy + \textsc{Cplex}} we decided to set up $K = \lceil 0.05 \cdot n \rceil$.

     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
            \item 4 heuristic approaches:
           \begin{itemize}
           	\item two pure greedy methods, guided by $g_1$ and $g_2$, labeled as \textsc{Greedy-1}, \textsc{Greedy-2}, respectively;
            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item two \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy-1}+\textsc{Cplex} and 
            \textsc{Greedy-2}+\textsc{Cplex}. 
        \end{itemize}
    \end{itemize}

@@

     \begin{table}[]
     	\centering
     	 \scalebox{0.85}{
     	\begin{tabular}{l|lllllll} \hline
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & 15.93  & 0.15    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 16.04  & 98.22   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 22.63  & 0.00    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
     		\textsc{Greedy-2}          & 19.97  & 0.00    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.07    & 21.19     & 2/97      & 0.30    & 57/97      & 0.06     \\
     		   \textsc{Greedy-2+Cplex} & 18.39  & 0.00    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
     	\end{tabular}}
     \end{table}

      \begin{table}[]
      	\centering
      	\scalebox{0.85}{
      	\begin{tabular}{l|lllllll} \hline
      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &  $ \bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & 36.03  & 0.00    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Cp}               & 36.03  & 18.95   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Greedy-1}             & 39.28  & 0.00    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
      		\textsc{Greedy-2}          & 40.92  & 0.00    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.01    & 19.41     & 4/97      & 0.21    & 19/97      & 0.08     \\
      		   \textsc{Greedy-2+Cplex} & 37.31  & 0.00    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
      	\end{tabular}}
      \end{table}

     \begin{table}[]
      \centering
       \scalebox{0.85}{
     	\begin{tabular}{l|lllllll} \hline
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & 2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
     		\textsc{Greedy-2}          & 3.52   & 0.32    & 6.61      & 2/97      & 0.10    & 28/97      & 0.08     \\
     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & 0.08    & 25/97      & 0.04     \\
     		   \textsc{Greedy-2+Cplex} & 3.32   & 0.33    & 6.81      & 6/97      & 0.08    & 25/97      & 0.04  \\ \hline   
     	\end{tabular}}
     \end{table}

    \begin{table}[]
    	\centering
    	\scalebox{0.85}{
 	  \begin{tabular}{l|lllllll} \hline
 		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
 		\textsc{Cplex}            & 6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Cp}               & 6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Greedy-1}             & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		\textsc{Greedy-2}          & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		   \textsc{Greedy-1+Cplex}  & 6.73   & 0.32    & 6.45      & 96/97     & 0.01    & 96/97      & 0.03     \\
 		   \textsc{Greedy-2+Cplex} & 7.42   & 0.31    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
 	\end{tabular}}
   \end{table}

        From the numerical results, we observe the following conclusions:
        \begin{itemize}
        	\item  For the topollogically--based benchmarks and the exact approaches, \textsc{Cplex} achieved best results among other approaches. moreover, \textsc{Cplex} could prove optimallity of all (192) instances, while \textsc{Cp} could not. It is expecially noticed for small polygons, where it seems hard for \textsc{Cp} to prove optimality.
        	\item For the point--based benchmark set and the exact approaches, \textsc{Cplex} again show its power, since it could prove all instances to optimallity, which is also the case of \textsc{Cp}.
        	\item  For the topollogically--based benchmarks and the heuristic approaches\fxnote{TODO...}
        \end{itemize}
          \fxnote{TODO: Milan: generisati plotove za vremena svakog od algoritama, takodje generisati plotove koji pokazuju procenat pokrivenosti optimalnih rjesenja CPLEX-a...}
